xwMOOC 딥러닝

### 2020-06-12 r-keras-mnist.Rmd
update r keras mnist

## 5.2. 모형 아키텍쳐 구성
model %>%
  layer_conv_2d(filters = 32, kernel_size = c(3,3), activation = 'relu',
                input_shape = input_shape) %>% 
  layer_conv_2d(filters = 64, kernel_size = c(3,3), activation = 'relu') %>% 
  layer_max_pooling_2d(pool_size = c(2, 2)) %>% 
  layer_dropout(rate = 0.25) %>% 
  layer_flatten() %>% 
  layer_dense(units = 128, activation = 'relu') %>% 
  layer_dropout(rate = 0.5) %>% 
  layer_dense(units = num_classes, activation = 'softmax')

    # layer_dense(units=256, activation="relu", input_shape=c(784))  %>%
    # layer_dropout(rate=0.4) %>%
    # layer_dense(units = 128, activation = "relu") %>%
    # layer_dropout(rate=0.4) %>%
    # layer_dense(units=10,activation="softmax")

>>>>

## 5.2. 모형 아키텍쳐 구성
model %>%
    layer_dense(units=256, activation="relu", input_shape=c(784))  %>%
    layer_dropout(rate=0.4) %>%
    layer_dense(units = 128, activation = "relu") %>%
    layer_dropout(rate=0.4) %>%
    layer_dense(units=10,activation="softmax")
